---
title: "README"
author: "Jordan DeHerrera"
date: "April 3, 2017"
always_allow_html: yes
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shinyBoots)
library(purrr)
```

## R Markdown

The shinyBoots package contains functions that fall into the following general categories:

* Functions to create boostrap elements

* Functions to create a reactive app with CRUD functions (create, retrieve, update, and delete)

* Functions to create charts and visualizations

* Functions to handle CSV files in a Shiny app

* Functions to manipulate data.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## Sample Drilldown Chart

```{r cars, warning=FALSE, message=FALSE}
df <- data.frame(
 name = c("Toyota", "Ford", "Volkswagen", "Cats", "Dogs", "Cows", "Sheep", "Pigs", "Apple", "Oranges"),
 value = c(4, 2, 2, 4, 3, 1, 2, 1, 4, 2),
 id = c(rep("cars",3), rep("animals",5), rep("fruits",2)),
 stringsAsFactors = FALSE
 )
createDrilldown(df,"id","Drilldown Test","Some additional text here for subtitle")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
